SPARQL on the open, decentralised Web

### 2016-06-05 dissertation/problems.tex
note HTTP/2 on cost of requests
typo

Finally, the intention was to bring convergence to the topics of this
thesis around a system to cache results that could be reused in
subsequent queries. As noted in Section~\ref{sec:motivcache}, this was
motivated by opportunity as well as problems, but it is intended to
address
problems~\ref{prob:syntacticcache}~and~\ref{prob:cachecartesian}.
Triple Pattern Fragments shifts most of the processing from servers to
clients, but Problem~\ref{prob:microcontrollers} makes that in some
cases infeasible.  In addition,
problems~\ref{prob:zipf}~and~\ref{prob:uniform} are compounded by
Problem~\ref{prob:nostats}, but alleviated somewhat by the presence of
cardinality estimates given by Triple Pattern Fragments, which we
exploit.

@@

Problem~\ref{prob:tpf} was along with
problems~\ref{prob:sparqlcomplex},~\ref{prob:endpointunpred}~and~\ref{prob:syntacticcache}
part of the motivation of \cite{ldf1} and \cite{verborgh2014querying},
and this builds in part on the insight I contributed when addressing
Problem~\ref{prob:lapis}. Their solution was to define an ontology to
describe an interface that can answer a single triple pattern, but
since it is hypermedia, it can be described in the messages of the
protocol. However, the solution in \cite{verborgh2014querying} does
not take into account Problem~\ref{prob:microcontroller}, so query
planning that shifts the burden to a cost-model driven balance between
server, proxy and client is an interesting direction.

>>>>

Finally, the intention was to bring convergence to the topics of this
thesis around a system to cache results that could be reused in
subsequent queries. As noted in Section~\ref{sec:motivcache}, this was
motivated by opportunity as well as problems, but it is intended to
address
problems~\ref{prob:syntacticcache}~and~\ref{prob:cachecartesian}.
Triple Pattern Fragments shifts most of the processing from servers to
clients, but Problem~\ref{prob:microcontroller} makes that in some
cases infeasible.  In addition,
problems~\ref{prob:zipf}~and~\ref{prob:uniform} are compounded by
Problem~\ref{prob:nostats}, but alleviated somewhat by the presence of
cardinality estimates given by Triple Pattern Fragments, which we
exploit.

@@

Problem~\ref{prob:tpf} was along with
problems~\ref{prob:sparqlcomplex},~\ref{prob:endpointunpred}~and~\ref{prob:syntacticcache}
part of the motivation of \cite{ldf1} and \cite{verborgh2014querying},
and this builds in part on the insight I contributed when addressing
Problem~\ref{prob:lapis}. Their solution was to define an ontology to
describe an interface that can answer a single triple pattern, but
since it is hypermedia, it can be described in the messages of the
protocol. However, the solution in \cite{verborgh2014querying} does
not take into account Problem~\ref{prob:microcontroller}, so query
planning that shifts the burden to a cost-model driven balance between
server, proxy and client is an interesting direction. In this context,
it should be noted that HTTP/2 \cite{rfc7540} is intended to make
multiple requests less expensive, and it is interesting to study the
practical impact of this as it could impact the cost of making many
HTTP requests substantially.
